StreamReduce: A Data Stream Processor with MapReduce Parallelism

### 2012-05-11 paper/paper.tex
Last edits

\subsection{Precision and Recall}
For task killing to be an effective strategy for a top-k computation, the
distribution of words in the corpus must be able to sustain data loss. This is the case
if the distribution is long-tailed, but is not true if the distribution is uniform.

@@

Because the word distribution is so skewed toward the head, there is a great potential to
speed up the calculation by killing tasks without having to sacrifice too much accuracy.
Additionally, Table~\ref{table:runtime} shows that the most significant time savings comes
from increasing the kill rate and keeping the work level high yields about a~20 percentage
point
increase in $F_{0.5}$-score.

>>>>

\subsection{Precision and Recall}
For task killing to be an effective strategy in a top-k computation, the
distribution of words in the corpus must be able to sustain data loss. This is the case
if the distribution is long-tailed, but is not true if the distribution is uniform.

@@

Because the word distribution is so skewed toward the head, there is a great potential to
speed up the calculation by killing tasks without having to sacrifice too much accuracy.
Table~\ref{table:top10} demonstrates how little the top~10 changes in response to varying
the job parameters.
Additionally, Table~\ref{table:runtime} shows that the most significant time savings comes
from increasing the kill rate and keeping the work level high yields about a~20 percentage
point
increase in $F_{0.5}$-score.
